Hybrid platforms and bargaining power

### 2023-12-16 src/paper/application.tex
Switch to numeric integration

\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1.csv}\equilibriumProfitOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5.csv}\equilibriumFullSurplusOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1.csv}\equilibriumFullSurplusTwoSided

@@

>>>>

\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-0.3.csv}\equilibriumFullSurplusOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5_lambda-1.csv}\equilibriumFullSurplusOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-1.csv}\equilibriumFullSurplusTwoSided

@@

The catch is that, in this comparative statics exercise, the platforms' increased product variety came out of thin air.
Specifically, when looking at the platform's profits, this increase in product variety is not associated with any increase in investment costs.
If we were to include those at the same level of the fringe's investment costs, then the platform's profits would be decreasing in $N_P$, and it would not make the investment.
Nevertheless, if it were to make it for some reason, it would not have the negative consequences that it had in \cref{sec:example}.
